\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-04 doc/sw-system.tex

\section{Classification Analysis}
\label{sec:swap}

In this section we outline our methodology for interpreting the interactions
of the volunteers with the identification interface.  Each classification made
is logged in a database, storing subject IDs, (anonymous) volunteer IDs, a
timestamp and the classification results.  The {\it kind} of subject --
whether it is a training subject (a  simulated lens or a known non-lens) or a
test subject (an unseen image drawn from the survey) -- is also recorded. For
all subjects, the positions of all Markers are recorded, in pixel coordinates.
For training subjects, we also store the ``classification'' of the subject as
a lens, or a non-lens, and also the type of object present in the image. These
types are summarized in \Tref{tab:objecttypes}.  This classification is used
to provide instant feedback, but is also the basic measurement used in a
probabilistic classification of every subject based on all image views to
date.

@@

In the next section we present results in terms of all three of these
probabilities, as we investigate the performance of the \SW system.

@@

% Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
% contributed. Correlation with number of classifications. 
% 
% PL and PD as measures of skill. not quite talent, due to possibility of
% learning - but agents assume talent. Performance of crowd re PD and PL.
% Correlations with N classifications.

>>>>

\section{Classification Stages and Analysis}
\label{sec:swap}

In this section we outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project.

Each classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results.  The
{\it kind} of subject -- whether it is a training subject (a  simulated lens
or a known non-lens) or a test subject (an unseen image drawn from the survey)
-- is also recorded. For all subjects, the positions of all Markers are
recorded, in pixel coordinates. For training subjects, we also store the
``classification'' of the subject as a lens, or a non-lens, and also the type
of object present in the image. These types are summarized in
\Tref{tab:objecttypes}.  This classification is used to provide instant
feedback, but is also the basic measurement used in a probabilistic
classification of every subject based on all image views to date.

@@

In \Sref{sec:results} below, we define several quantities based on the 
probabilities listed above that serve to quantify the performance of the crowd
in terms of the information they provide via their classifications, and report
on the performance of the system in returning a sample of lens candidates
as a function of $\pr(\LENS|C,T)$ threshold.

During stage 1 classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them.
The analysis code was run every night during the project, and subjects retired
in batches after its completion. This introduced some inefficiency, because
some classifications were accumulated in the time between them crossing the
rejection threshold and the subject actually being retired from the website.
As subjects were retired from the site, more subjects were activated. In this
way, the volunteers who down-voted images for not containing any lensed
features enabled new images to be shown to other members of the community.

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each.

@@
